Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2021-10-12 paper/manuscript.Rmd
Clarification of amphibians
Add info about trophic downgrading

It is critical to establish whether or not functional loss is the general rule for communities.
While functional loss is frequently cited as one of the most pressing concerns of the anthropocene [@cardinale2012; @dirzo2014; @young2016], it is not necessarily inevitable even in scenarios of species loss [@daz2001].
Forecasts of functional loss range from negligible [@gallagher2013] to dire [@petchey2002; @pimiento2020].
And while some observed trends show significant functional loss [@flynn2009] others document no loss even in some of the most heavily impacted communities [@edwards2013; @matuoka2020].
On paleoecological time scales functional composition shows mixed responses to environmental change and extinction events [@jackson2015; @dornelas2018], with significant impacts of species extinctions on functional diversity in some taxa and not others [@pimiento2017].

@@

Our final dataset included 2,443 time series from 53 studies in 21 countries and 15 biomes and 13 different traits (Fig 1).
The earliest sample was in 1923 and the most recent was in 2016.
Only four studies (consisting of 11 time series) came from Amphibian studies due to the limited availability of amphibian time series and low species richness values for assemblages (Table 1).
For a full breakdown of studies and their characteristics, see the supplement.

>>>>

It is critical to establish whether or not functional loss is the general rule for communities.
While functional loss is frequently cited as one of the most pressing concerns of the anthropocene [@cardinale2012; @dirzo2014; @young2016], it is not necessarily inevitable even in scenarios of species loss [@daz2001]. Forecasts of functional loss range from negligible [@gallagher2013] to dire [@petchey2002; @pimiento2020]. And while some observed trends show significant functional loss [@flynn2009] others document no loss even in some of the most heavily impacted communities [@edwards2013; @matuoka2020]. On paleoecological time scales functional composition shows mixed responses to environmental change and extinction events [@jackson2015; @dornelas2018], with significant impacts of species extinctions on functional diversity in some taxa and not others [@pimiento2017]. Some losses of functional diversity are indisputable on both paleocological and contemporary timescales such as continued trophic downgrading due to loss of large-bodied mammals, but implications of those losses for local diversity patterns are less clear [@estes2011; @smith2018] .

@@

Our final dataset included 2,443 time series from 53 studies in 21 countries and 15 biomes and 13 different traits (Fig 1).
The earliest sample was in 1923 and the most recent was in 2016.
Only four studies (consisting of 11 time series) came from Amphibian studies due to the limited availability of amphibian time series and low species richness values for assemblages (Table 1).
Amphibians are of particular concern due to impacts of habitat loss and pollution [@gibbons2000], so we include the data we have while acknowledging that general inference for Amphibians as a taxa is not possible with the timeseries available.
For a full breakdown of studies and their characteristics, see the supplement.
